Testing Efficacy; Insights from a Simple Epidemic Model

### 2020-11-13 SIR_manuscript.tex
model was updated

\begin{align}
\label{model}
 d S_u/dt &= -\Lambda S_u - F_S S_u + \omega S_n \\
 d S_n/dt &= -\Lambda S_n + (1-p_S) F_S S_u - \omega S_n \\
 d S_p/dt &= -\Lambda S_p + p_S F_S S_u - \omega S_p \\
 d S_t/dt &= -\Lambda S_t + \omega S_p \\
 d I_u/dt &= \Lambda S_u - F_I I_u + \omega I_n  - \gamma I_u  \\
 d I_n/dt &= \Lambda S_n + (1-p_I) F_I I_u - \omega I_n -\gamma I_n \\
 d I_p/dt &= p_I F_I I_u - \omega I_p -\gamma I_p \\
 d I_t/dt &= \omega I_p - \gamma I_t  \\
 d R_u/dt &= \gamma I_u - F_R R_u + \omega R_n \\
 d R_n/dt &= \gamma I_n + (1-p_R) F_R R_u - \omega R_n  \\
 d R_p/dt &= \gamma I_p + p_R F_R R_u  - \omega R_p  \\
 d R_t/dt&= \gamma I_t + \omega R_p  \\
 dN/dt &= \omega (S_n + I_n + R_n)   \\
 dP/dt &= \omega(I_p + R_p).
\end{align}

>>>>

\begin{align}
\label{model}
 d S_u/dt &= -\Lambda S_u - F_S S_u + \omega S_n \\
 d S_n/dt &= -\Lambda S_n + (1-p_S) F_S S_u - \omega S_n \\
 d S_p/dt &= -\Lambda S_p + p_S F_S S_u - \omega S_p \\
 d S_t/dt &= -\Lambda S_t + \omega S_p \\
 d I_u/dt &= \Lambda S_u - F_I I_u + \omega I_n  - \gamma I_u  \\
 d I_n/dt &= \Lambda S_n + (1-p_I) F_I I_u - \omega I_n -\gamma I_n \\
 d I_p/dt &= \Lambda S_p + p_I F_I I_u - \omega I_p -\gamma I_p \\
 d I_t/dt &= \Lambda S_t + \omega I_p - \gamma I_t  \\
 d R_u/dt &= \gamma I_u - F_R R_u + \omega R_n \\
 d R_n/dt &= \gamma I_n + (1-p_R) F_R R_u - \omega R_n  \\
 d R_p/dt &= \gamma I_p + p_R F_R R_u  - \omega R_p  \\
 d R_t/dt&= \gamma I_t + \omega R_p  \\
 dN/dt &= \omega (S_n + I_n + R_n)   \\
 dP/dt &= \omega(I_p + R_p).
\end{align}
